---
title: "Toadfish ETH"
author: "Alex Dornburg"
date: "August 18, 2017"
output: html_document
---

###part 1
## Toadfish Swimbladder Multiple Regression

Now testing swimbladder mass against each organ in males (liver, brain, heart, gonads, and the sum of liver brain heart) with log10 eviscerated mass as a covariate

```{r toads2}
dyn.load('/Library/Java/JavaVirtualMachines/jdk1.8.0_40.jdk/Contents/Home/jre/lib/server/libjvm.dylib')
library(rJava)
library(xlsx)
read.xlsx(file="Data_Here", sheetIndex=1)->toads
males <- subset(toads, M.F=="m")
###LIVER
lm(log(males$swim.weight)~log(males$liver.weight)*log(males$weight.evi),data = males)->tta
summary(tta)
confint(tta,level=0.95)[4,]->liverconf
coef(tta)[4]->livermean

###BRAIN
lm(log(males$swim.weight)~log(males$brain.weight)*log(males$weight.evi),data = males)->tta2
summary(tta2)
confint(tta2,level=0.95)[4,]->brainconf
coef(tta2)[4]->brainmean

###HEART
lm(log(males$swim.weight)~log(males$heart.weight)*log(males$weight.evi),data = males)->tta4
summary(tta4)
confint(tta4,level=0.95)[4,]->heartconf
coef(tta4)[4]->heartmean

###GONADS
lm(log(males$swim.weight)~log(males$gonad.weight)*log(males$weight.evi),data = males)->tta5
summary(tta5)
confint(tta5,level=0.95)[4,]->gonadconf
coef(tta5)[4]->gonadmean

###COMBINED LIVER BRAIN HEART
males$heart.weight+males$brain.weight+males$liver.weight->combined_weights
lm(log(males$swim.weight)~log(combined_weights)*log(males$weight.evi),data = toads)->tta6
summary(tta6)
confint(tta6,level=0.95)[4,]->combinedconf
coef(tta6)[4]->combinedmean

####
#Make a plot of regression slopes
c(liverconf[1],brainconf[1],heartconf[1],gonadconf[1],combinedconf[1])->lower
c(liverconf[2],brainconf[2],heartconf[2],gonadconf[2],combinedconf[2])->upper
c(livermean,brainmean,heartmean,gonadmean,combinedmean)->means
c(1,2,3,4,5)->y

plot(0,type='n',axes=FALSE,ann=FALSE)
plot(means,y, new=FALSE, xlim=c(-0.2,0.2))
arrows(means,y,lower,y, angle=90)
arrows(means,y,upper,y,angle=90)
abline(v=0)
```

## Now lets look at regression coefficients and do the above much more efficiently while we are at it
```{r toads2_Regression_coeff}
dyn.load('/Library/Java/JavaVirtualMachines/jdk1.8.0_40.jdk/Contents/Home/jre/lib/server/libjvm.dylib')
library(rJava)
library(xlsx)
read.xlsx(file="Data_Here", sheetIndex=1)->toads
males <- subset(toads, M.F=="m")
log(males$swim.weight)->swim
log(males$gonad.weight)->gonad
log(males$liver.weight)->liver
log(males$brain.weight)->brain
log(males$heart.weight)->heart
log(males$weight.evi)->body
log(males$heart.weight+males$brain.weight+males$liver.weight)->combined

cbind(swim,gonad,liver,brain,heart,body,combined)->data2
as.data.frame(data2)->data2.0
#function for plotting
plot_coeffs <- function(mlr_model) {
      coeffs <- coefficients(mlr_model)
      mp <- barplot(coeffs, col="#3F97D0", xaxt='n', main="Regression Coefficients")
      lablist <- names(coeffs)
      text(mp, par("usr")[3], labels = lablist, srt = 45, adj = c(1.1,1.1), xpd = TRUE, cex=0.6)
      return(coeffs)
    }


model <- lm(swim ~ .*body, data = data2.0)
plot_coeffs(model)

coeffs2 <- coefficients(model)
mp <- barplot(c(coeffs2[2],coeffs2[3],coeffs2[4],coeffs2[5],coeffs2[7],coeffs2[8],coeffs2[9],coeffs2[10],coeffs2[11],coeffs2[12]),col="#3F97D0", xaxt='n', main="Regression Coefficients")
      text(mp, par("usr")[3], labels = c("gonad","liver","brain","heart","combined","gonad:body","liver:body","    brain:body","heart:body","body:combined"), srt = 45, adj = c(1.1,1.1), xpd = TRUE, cex=0.6)

summary(model)
```

### Option 2, The residual regressions and Kendall rank correlation

```{r toads2_Residual_part}
dyn.load('/Library/Java/JavaVirtualMachines/jdk1.8.0_40.jdk/Contents/Home/jre/lib/server/libjvm.dylib')
library(rJava)
library(xlsx)
read.xlsx(file="Data_Here", sheetIndex=1)->toads
males <- subset(toads, M.F=="m")

log(males$swim.weight)->swim
log(males$gonad.weight)->gonad
log(males$liver.weight)->liver
log(males$brain.weight)->brain
log(males$heart.weight)->heart
log(males$weight.evi)->body
log(males$heart.weight+males$brain.weight+males$liver.weight)->combined

##Datasets are different sizes so we need to make each pair here to omit missing data properly

cbind(swim,gonad,body)->sg
na.omit(sg)->sg
cbind(swim,liver,body)->sl
na.omit(sl)->sl
cbind(swim,brain,body)->sb
na.omit(sb)->sb
cbind(swim,heart,body)->sh
na.omit(sh)->sh
cbind(swim,combined,body)->scombined
na.omit(scombined)->scombined

#get residuals for swimbladder for each dataset
lm(sg[,1]~sg[,3])->swimg
lm(sl[,1]~sl[,3])->swiml
lm(sb[,1]~sb[,3])->swimb
lm(sh[,1]~sh[,3])->swimh
lm(scombined[,1]~scombined[,3])->swimcombined

lm(sg[,2]~sg[,3])->gonad2
lm(sl[,2]~sl[,3])->liver2
lm(sb[,2]~sb[,3])->brain2
lm(sh[,2]~sh[,3])->heart2
lm(scombined[,2]~scombined[,3])->combined2

#analyses and kendall's correlation
lm(resid(swimg)~resid(gonad2))->swim_gonad
cor.test(resid(swimg), resid(gonad2), method="kendall")
summary(swim_gonad)

lm(resid(swiml)~resid(liver2))->swim_liver2
cor.test(resid(swiml), resid(liver2), method="kendall")
summary(swim_liver2)

lm(resid(swimb)~resid(brain2))->swim_brain2
cor.test(resid(swimb), resid(brain2), method="kendall")
summary(swim_brain2)

lm(resid(swimh)~resid(heart2))->swim_heart2
cor.test(resid(swimh), resid(heart2), method="kendall")
summary(swim_heart2)

lm(resid(swimcombined)~resid(combined2))->swim_combined2
cor.test(resid(swimcombined), resid(combined2), method="kendall")
summary(swim_combined2)

```

###Option 3  Multivariate regression


```{r toads2_option3}
dyn.load('/Library/Java/JavaVirtualMachines/jdk1.8.0_40.jdk/Contents/Home/jre/lib/server/libjvm.dylib')
library(rJava)
library(xlsx)
library(Hmisc)
read.xlsx(file="Data_Here", sheetIndex=1)->toads
males <- subset(toads, M.F=="m")

log(males$swim.weight)->swim
log(males$gonad.weight)->gonad
log(males$liver.weight)->liver
log(males$brain.weight)->brain
log(males$heart.weight)->heart
log(males$weight.evi)->body
log(males$heart.weight+males$brain.weight+males$liver.weight)->combined
cbind(swim,gonad,liver,brain,heart,body,combined)->data2
na.omit(data2)->noNAdata

lm(cbind(noNAdata[,1],noNAdata[,2],noNAdata[,3],noNAdata[,4],noNAdata[,5],noNAdata[,7])~noNAdata[,6])->multi_var

summary(multi_var)->sums
resid(multi_var)->resids
as.matrix(resids)->resids
colnames(resids)<-c("swim","gonad","liver","brain","heart","combined")
res2 <- cov(resids)
res2
cov2cor(res2)->correlations
correlations

rcorr(correlations)->coco

library(corrplot)
corrplot(correlations, type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)

 #not significant correlations are blank 
corrplot(coco$r, type="upper", order="hclust", p.mat = coco$P, sig.level = 0.01, insig = "blank")

#P-value visual
corrplot(coco$r, type="upper", order="hclust", p.mat = coco$P, sig.level = 0.01, insig = "p-value")

```